Rodent trapping to explore rodent ecology and zoonotic disease risk: A scoping review

### 2021-08-26 reports/manuscript.Rmd
Adding imputed trapnights

---
title: "Rodent trapping to explore rodent ecology and zoonotic disease risk: A scoping review"
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---

>>>>

---
title: "Rodent trapping to explore rodent ecology and zoonotic disease risk: A scoping review"
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  # distill::distill_article:
  #   toc: true
  #   toc_depth: 3
  #   toc_float: true
  word_document
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---
